---
title       : Football World Cup data
subtitle    : Percentage wins
author      : MD
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [shiny, interactive, bootstrap]
mode        : selfcontained # {standalone, draft
knit        : slidify::knit2slides
---

## Slide 2: Background

1. Aim: To produce a simple R Shiny application
2. Concept: An application that displays the percentage of matches won in the Football World Cup
3. Detail: The data will be displayed as:
        a) A plot of percentage wins by all countries within a tournament; or 
        b) A plot of percentage winds by a single country across all years
4. Data downloaded from: 
        http://www.theguardian.com/news/datablog/2010/may/05/world-cup-historical-statistics


--- .class #id 

## Slide 3: Example plot of each countries' performance within a tournament (e.g. 1966)

```{r echo = F, results = 'asis', fig.height=6, fig.width=8}

library(ggplot2)
data<-read.csv("world_cup_data.csv")
names(data) <- c("Year","Team", "ISO.code","Goals.for", "Goals.against", "Penalties","Matches", "Shots.on.goal", "Shots.wide", "Free.kicks", "Offside","Corners", "Won", "Drawn", "Lost")
# Year <- unique(sort(data$Year))
# Country <- unique(sort(data$Team))
data_sub<-subset(data, Year == "1966")                                
p <- ggplot(data_sub, aes(x = Team, y = (Won/(Won+Drawn+Lost)*100))) + geom_bar(stat = "identity")+
        scale_fill_manual("", values=c("target"="darkgrey","try"="blue"))+
        scale_y_continuous(breaks=seq(0,100,10),limits=c(0,100),"% Matches won")+
        theme(axis.title.x = element_text(size = 14, vjust = -1))+
        theme(axis.title.y = element_text(size = 14, angle=90, vjust=0))+
        theme(axis.text.x = element_text(size = 10,colour="black",vjust = 0, angle = 90))+
        theme(axis.text.y = element_text(size = 12,colour="black"))
        print(p)
```

--- .class #id 

## Slide 4: Example plot of a single country (e.g. England) over all the year of the World Cup (data: 1930 - 2006)

```{r echo = F, results = 'asis', fig.height=6, fig.width=8}

library(ggplot2)
data<-read.csv("world_cup_data.csv")
names(data) <- c("Year","Team", "ISO.code","Goals.for", "Goals.against", "Penalties","Matches", "Shots.on.goal", "Shots.wide", "Free.kicks", "Offside","Corners", "Won", "Drawn", "Lost")
# Year <- unique(sort(data$Year))
# Country <- unique(sort(data$Team))
data_sub<-subset(data, Team == "England")                                
p <- ggplot(data_sub, aes(x = Year, y = (Won/(Won+Drawn+Lost)*100))) + geom_bar(stat = "identity")+
        scale_fill_manual("", values=c("target"="darkgrey","try"="blue"))+
        scale_y_continuous(breaks=seq(0,100,10),limits=c(0,100),"% Matches won")+
        scale_x_continuous(breaks=seq(1930,2010,4), limits=c(1930,2010),"Year")+
        theme(axis.title.x = element_text(size = 14, vjust = -1))+
        theme(axis.title.y = element_text(size = 14, angle=90, vjust=0))+
        theme(axis.text.x = element_text(size = 10,colour="black",vjust = 0, angle = 90))+
        theme(axis.text.y = element_text(size = 12,colour="black"))
        print(p)
```

--- &interactive

## Slide 5: Example calculation of percentage of matches won

```{r opts.label = 'interactive', results = 'asis'}
matches_won<-5
matches_drawn<- 2
matches_lost <- 2
matches_played <- matches_won+matches_drawn+matches_lost
percentage_wins <- as.integer((matches_won/matches_played)*100)
result <-paste("Percentage of matches won = " , percentage_wins)
barplot(percentage_wins, ylim=c(0,100), main = "% wins")
```


